\documentclass[a4paper]{article}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{setspace}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\vspace*{5pt}
\begin{flushleft}
\noindent {\href{https://yadavdeepak95.github.io}{\huge\textbf{Deepak Yadav}}}\\
\vspace{-25pt}
\hfill \faPhone +91-9958124967
\end{flushleft}
\vspace{-5pt}\hfill \faEnvelope-\href{mailto:dpkyadav@cse.iitk.ac.in}{dpkyadav@cse.iitk.ac.in}\\
Department of Computer Science and Engineering \hfill \faGithub-\href{https://github.com/yadavdeepak95}{yadavdeepak95} \faLinkedin-\href{https://www.linkedin.com/in/yadavdeepak95/}{yadavdeepak95}
\vspace{-6pt}
\\
\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{7.4cm}|p{6.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\

\hline
\centering{2018-present}& \centering{M.Tech(Computer Science \& Engineering)} & \centering{Indian Institute of Technology, Kanpur} & 8.86/10\\
\hline
\centering{2012-2016}& \centering{
B.Tech(Mechanical Engineering)} & \centering{MRCE, Faridabad(MDU, Rohtak)} & 70.1$\%$\\
\hline
\centering{2012} & \centering{CBSE(\Romannum{12})} & \centering{D A V Public School} & 81.16$\%$\\
\hline
\centering{2010} & \centering{CBSE(\Romannum{10})} & \centering{D A V Public School} & 8.2/10\\
\hline
\end{tabular}
\end{center}
% {\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}

{\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}
\begin{itemize}
\item 2018 Secured \textbf{99.52} percentile in Graduate Aptitude Test in Engineering (GATE)
\item 2018 Received \textbf{Scholarship} for Google India Challenge Scholarship for the Android Basics track
\item 2011 Secured \textbf{144 state rank} in  Math Olympiad(International Olympiad of Mathematics'11)

\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Work Experience}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Tata Consultancy Services, Mumbai IN } \hfill\hfill(\textit{Jan'17\textendash July'18})\\\textbf{Designation: }\textbf{Assistant System Engineer}
\begin{itemize}
\item Automated the price update functionality  of products in Lotus Notes, which saved around 30 hours of work per update. 
\item Involved in the development of new functionality which allows offline order entry by Customer Sales Representative in IBM WebSphere Commerce, which improved customer satisfaction.
% \item Production support of IBM’s sales center application, WCS and Lotus Notes application for the existing functionality.
\end{itemize}\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Thesis and Projects}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Asynchronous Consensus Protocol (M.Tech Thesis)} \hfill\hfill(\textit{May'18\textendash     Ongoing})\\
\textbf{Mentor: }\textbf{Prof Sandeep K. Shukla } 
\begin{itemize}
\item \textbf{Aim}: To Implement Asynchronous Consensus Protocol in Hyperledger Fabric to increase the robustness of Blockchain.
\item %Studied various consensus protocols and 
Working on designing and implementing the algorithm of Asynchronous Consensus Protocol for Hyperledger Fabric.
\end{itemize}
\item \textbf{Certificate Storage and Verification System}  \hfill\hfill(\textit{Mar'19\textendash Apr'19})\\
\textbf{Mentor: }\textbf{Prof Sandeep K. Shukla}, Technologies Used: Hyperledger Composer, IPFS, Node Js, RESTful API
\begin{itemize}
\item Implemented blockchain solution that allows users to publish, download, and verify the authenticity of documents.
\item Developed a feature using smart contracts logic which prevents duplicate use of certificates by a user. 
\end{itemize}
\item \textbf{Loc Restro(Location-based Food Ordering Application)}\hfill\hfill(\textit{ Sept'18\textendash Nov'18})\\ \textbf{Mentor: }\textbf{Prof. T.V. Prabhakar}, Technologies Used: Ionic Framework, Mongo DB, Node Js
\begin{itemize}
\item Developed back-end of the hybrid app that based on user's location shows restaurants and allow a user to place an order.
\item Designed and implemented back-end of the system to be scalable, using Geo-location-based Load Balancing.
\end{itemize}
\item \textbf{Exploitation and Defence of Computer Systems} \hfill\hfill(\textit{Feb'19\textendash Mar'19})\\
\textbf{Mentor: Prof. Pramod Subramanyan}
\begin{itemize}
\item \textbf{Securing Zoobar Server} Technologies used: Python, gdb\\
Exploited vulnerabilities using control hijacking techniques like buffer overflow and format string attacks. Fixed security bugs in web server, implemented privilege separation %and
server-side, sand-boxing of executable profiles in the okws server.
\item \textbf{Encrypted Storage System}, Technology Used: Golang\\
Designed and Developed a Key-Value store which ensured the integrity, confidentiality, and secure sharing of data.
\end{itemize}
\item \textbf{Pocket ML (Machine Learning Model for Small Devices)} \hfill\hfill(\textit{Aug'19\textendash Dec'19})\\
\textbf{Mentor: Prof. Piyush Rai}, Technologies used: Python, scikit-learn
\begin{itemize}
\item Studied Pruning Random Forests for Prediction on a Budget by Feng Nan et al. and Benchmarked SVM's accuracy with different kernels (Liner, RBF, Polynomial) on various data set like IRIS, MNIST, USPS.
\end{itemize}
\end{itemize}
\vspace{-2mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}
% \section{Skills}
% \textbf{Programming:}\\
% Java \textbullet{}   C++ \textbullet{} Python\\
% \textbf{Web:}\\
% HTML  \textbullet{}CSS  \textbullet{}Javascript\\
% \textbf{Utilities}\\
% Linux Shell Utilities\textbullet{} Git\textbullet{} GDB\textbullet{} L A TEX
%\end{itemize}Java, Javascript, Shell script, Nodejs, Matlab, HTML, Android, MongoDB, Oracle SQL, PL/SQL,Kernel module programming, ML libraries: pydub, nltk, scikit-learn, gensim, keras, tensorflow

{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Programming Languages: }C/C++, Java, Go, 
\item \textbf{Tools and Technologies: } Linux Shell Utilities, Git, Javascript, Python, Android, MongoDB, MySQL, \LaTeX
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Students' Senate Nominee, DPGC, IIT Kanpur}\hfill\hfill(\textit{Dec'18\textendash present})
\begin{itemize}
\item  Solved termination cases of 4 students with CPI less than the required CPI in the 1st year at Academic Senate.
%TODO ADD?

%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}
\item \textbf{Teaching Assistant, IIT Kanpur}\hfill\hfill(\textit{Aug'18\textendash Dec'18, Aug'19\textendash present})
\begin{itemize}
\item Fundamentals of Computing, ESC 101: Duties involved helping students in hands-on problem-solving in C \& grading.           \item  Software Architecture, CS 654: Major duties involved creation and grading of quizzes and assignments.



%\item Acted as a link between Placement core team, companies and Students during placement process.
\end{itemize}
\vspace{1mm}
\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Relevant Courses}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{p{6.2cm}p{6.1cm}p{6.1cm}}

o Analysis of Concurrent program&
o Topics in Distributed Systems&
o Computer Systems Security\\
o Introduction to Blockchain Technology&
o Intro to Machine Learning&
o Topics in Internet Technology\\


\end{tabular}
\end{center}
%\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\item 2018 Secured \textbf{2nd position} among 32 students in Systems Research Boot Camp held at IIT Kanpur.
\item 2015 Technical Team Member for Team AutoTregoan, Participated in Elite Karting, 2015 held in Bhopal, India.
\item 2013 and 2014 Trained around \textbf{50+ students} overhauling of Maruti 800 engine, single cylinder engine, and carburetor.
%  \item 2013 Diploma holder in MCAD(Auto-cad) and pro-E from Mitsu CAD Education Society.
\end{itemize}\newpage\newpage
\end{document}
